A search algorithm for the global extremum \break of a discontinuous function\thanks{This work was supported by the Russian Science Foundation, project No.\,21-11-00204.}

### 2021-10-01 2021/ICCS_BarkalovUsova/iccs.tex
one more correction in Russian

In this paper, we will consider a deterministic algorithm for solving global optimization problems with both given and unspecified discontinuity points. This algorithm was developed on the basis of the \textit{global search algorithm} proposed by Strongin \cite{Strongin2000} and provides a search for the global optimum. Section 2 describes the algorithm for functions with given discontinuities. Section 3 discusses how to identify unspecified discontinuities. Section 4 describes how this discontinuity detection method can be used in the original algorithm. Section 5 presents the results of a comparison of the developed algorithm with the global search methods implemented in MATLAB Global Optimization Toolbox \cite{MatlabOTB}. Section~6 concludes the paper.

@@

Note that the value of the difference $\mu_i$ for the interval containing the extremum point can be close to zero, which will lead to the fulfillment of the first inequality from (\ref{mu_main_cond}). To eliminate the effect of small relative differences of intervals containing extreme points, the additional constraint $1 \leq p < q(m-2(s+1))$ is introduced in (\ref{mu_main_cond}) to exclude small values of $\mu_i$ from consideration. 
%Russian
Значение параметра $q$ отражает априорные предполжения о том, какая доля поисковых интервалов в их общем числе не будет содержать точек локальных экстремумов.

>>>>

In this paper, we will consider a deterministic algorithm for solving global optimization problems with both given and unspecified discontinuity points. This algorithm was developed on the basis of the \textit{global search algorithm} proposed by Strongin \cite{Strongin2000} and provides a search for the global optimum. 
%Russian
Проводимое в статье рассмотрение ограничено одномерным случаем. Обобщение нового алгоритма на многомерный случай может быть выполнено в соответствии со ставшими уже стандартными подходами из \cite{Grishagin2016,Grishagin2018}, использующими adaptive nested optimization scheme. 
Указанная схема редукции размерности позволяет заменить решение исходной многомерной задачи решением семейства одномерных задач, рекурсивно связанных между собой.

Основная часть статьи организована следующим образом.

Section 2 describes the algorithm for functions with given discontinuities. Section 3 discusses how to identify unspecified discontinuities. Section 4 describes how this discontinuity detection method can be used in the original algorithm. Section 5 presents the results of a comparison of the developed algorithm with the global search methods implemented in MATLAB Global Optimization Toolbox \cite{MatlabOTB}. Section~6 concludes the paper.

@@

Note that the value of the difference $\mu_i$ for the interval containing the extremum point can be close to zero, which will lead to the fulfillment of the first inequality from (\ref{mu_main_cond}). To eliminate the effect of small relative differences of intervals containing extreme points, the additional constraint $1 \leq p < q(m-2(s+1))$ is introduced in (\ref{mu_main_cond}) to exclude small values of $\mu_i$ from consideration. 
%Russian
Параметр $0<q<1$ тажке задается исследователем. Значение $1 - q$ отражает априорные предполжения о том, какая доля поисковых интервалов будет иметь значения $\mu_i$ близкими к нулю, т.е. фактически характеризует степень многоэкстремальности задачи. В проведенных экспериментах использовалось значение $q=0.9$.
